%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {PhD in Computer Science} % Degree
    {University of St. Gallen} % Institution
    {St. Gallen, Switzerland} % Location
    {Oct. 2018 - Current} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Alternate Reality; Intuitive elicitation of interactions in pervasive (computing) environments for industrial domains.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Master of Media and Governance} % Degree
    {Keio University} % Institution
    {Kanagawa, Japan} % Location
    {Apr. 2016 - Mar. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {GPA: 4.0/4.0}
        \item {Received Mori Fund Scholarship from Keio Research Institute at SFC.}
        \item {Selected as Global Entrepreneurship Global Innovator Program Scholar by National Ministry of Education, Culture, Sports, Science and Technology.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {B.A. in Environment and Information Studies} % Degree
    {Keio University} % Institution
    {Kanagawa, Japan} % Location
    {Apr. 2011 - Mar. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {GPA: 3.8/4.0}
        \item {Joined Professor Dr. Jin Mitsugi's lab and Auto-ID Laboratory Japan (2013-Present).}
        \item {Joined Associate Professor Dr. Rodney Van Meter III's Advancing Quantum Architecture research group (2011-2014).}
        \item {Received Yamagishi Student Project Support Program Scholarship.}
        \item {Received Keio University Prize Fellowship.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {A.S. in Computer Science} % Degree
    {Bunker Hill Community College} % Institution
    {Boston, MA, U.S.A.} % Location
    {May. 2008 - Feb. 2010} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {GPA: 3.5/4.0}
        \item {Withdrew without degree due to health problem (Cluster Headache disease)}
        \item {Selected in the international exchange scholarship program to Institut Français des Alpes in Annecy, France.}
        \item {Has been honored Dean's list in 2009.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {A.A. in Liberal Arts} % Degree
    {Quinsigamond Community College} % Institution
    {Worcester, MA, U.S.A.} % Location
    {Sep. 2007 - May. 2008} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Transferred to Bunker Hill Community College.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
