%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Research Assistant} % Job title
    {University of St. Gallen} % Organization
    {St. Gallen, Switzerland} % Location
    {Oct. 2018 - Current} % Date(s)
    {
      \begin{cvitems}
        \item{Teaching assistant for a 6-ECTS course: Introduction to Computer Systems and Networks}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Researcher} % Job title
    {Keio Research Institute at SFC - Keio University} % Organization
    {Kanagawa, Japan} % Location
    {Apr. 2018 - Sep. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Robust and high-performance filtering engine and testing framework for ID-based inventory system including RFID and Barcode.}
        \item{Distributed EPCIS discovery and accessible framework for cross-border transactions (NEDO project).}
        \item{Supervision of several undergraduate/master students' graduation projects in Auto-ID Lab.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Research Assistant} % Job title
    {Sony Computer Science Laboratory} % Organization
    {Tokyo, Japan} % Location
    {Apr. 2015 - Mar. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Built and deployed overall service infrastructure utilizing Ansible automation and Docker container, focusing on high-availability, fault tolerance, and auto-scaling.}
        \item{Committed to various research projects including Smart-Grid energy distribution infrastructure (Open Energy System) prototyping and redundant power supply system design for Sony CSL's data center.}
        \item{Operated 7 network segments with 3 different upstreams administrating 30+ appliances for research projects in the lab.}
        \item{Integrated LDAP credential to multiple internal services with Websocket communication.}
        \item{Designed and developed Sony CSL Open House 2015 Website and registration management system.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Research Intern at Web of Things Research Group} % Job title
    {Siemens Corporation} % Organization
    {Berkeley, CA, U.S.A.} % Location
    {Oct. 2016 - May. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Designed and implemented a Mixed-Reality user interface prototype for robotic arm assembly on shop floor with Microsoft HoloLens.}
        \item{Developed a semantic backend system with industrial vocabularies in Siemens to operate equipment by providing intuitive propagates.}
        \item{Developed a middleware adapter for Open Source meta-operating system for robots (ROS) as well as tangible Mixed-Reality user interfaces for intuitive robot arm operation by bridging them to the semantic backend.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Engineering Intern at Video Distribution and Mobile Network R\&D group} % Job title
    {Cisco Systems, Inc.} % Organization
    {Milpitas, CA, U.S.A} % Location
    {Aug. 2013 - Jul. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Conducted portfolio and performance analysis of existing Cloud Stack(including Amazon Web Services, Google Computing Engine, Windows Azure and Rackspace) for building auto-scale online video frame encoders.}
        \item{Implemented and demonstrated Home Media Gateway for Video On Demand delivery and IPTV, exhibited in Cisco Live 2014.}
        \item{Evaluated multimedia stream quality on on-market hardware devices through LTE Mobile network.}
        \item{Demonstrated SDN + vGiLAN technology in Cisco Live 2014: enhancement in LTE network operation by realizing service module chaining (i.e., Deep Packet Inspection, Watermark override, Encryption, Bandwidth capping, etc...).}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Research Assistant} % Job title
    {Internet Initiative Japan Research Laboratory} % Organization
    {Tokyo, Japan} % Location
    {Sep. 2012 - July. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed Modbus M2M protocol adapter for Fluentd log aggregator to collect solar radiation sensor data from "freight-container" data center feasibility experiment.}
        \item {Developed Docker-based scalable load-balancer of overwhelming sensor data flow.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Teaching Assistant} % Job title
    {Keio University} % Organization
    {Kanagawa, Japan} % Location
    {Apr. 2012 - Current} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Mobile Network Theory with Prof. Dr. Jin Mitsugi.}
        \item {Computer Architecture with Assoc-Prof. Dr. Rodney Van Meter III.}
        \item {Data Structure and Programming with Prof. Dr. Jin Mitsugi.}
        \item {Exploring Environment and Information Studies with Prof. Dr. Jun Murai.}
        \item {Internet Measurement and Data Analysis with Dr. Kenjiro Cho (Visiting Senior Researcher).}
        \item {Big Data Processing with Assoc-Prof. Dr. Keisuke Uehara.}
        \item {Linear Algebra with Dr. Dominic Horsman (Visiting Senior Researcher).}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
