%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activity}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software \& Hardware Developer and Fieldworker} % Affiliation/role
    {Sake International Traceability Project with DSRI, IBM Japan, Toppan and Daiwa Computer} % Organization/group
    {Japan \& Thailand} % Location
    {2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Built a smart dolly with Antenna, RFID Reader, LED display, and Beagle Bone for automatic inventory of Japanese rice wine.}
        \item {Implemented traceability information system for international shipment.}
        \item {Conducted experiments on tamper resistant RFID seals readability in various conditions.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Lecturer of IoT design and prototyping} % Affiliation/role
    {EDGE Global Innovation Forum Spring 2015 Workshop} % Organization/group
    {Tokyo, Japan} % Location
    {Mar. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {IoT Workshop design with deployment of 20+ Intel Edison-based microservers with GPIO to actuate servo motors and sensor tags.}
        \item {Built data flow control mechanism for participants by MQTT messaging and Node-RED graphical interfaces.}
        \item {Built semi-automatic data graphing tool with Graphana and InfluxDB on IBM Bluemix Cloud Platform.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Representative} % Affiliation/role
    {Yaofuji Keio University Agricultural Group} % Organization/group
    {Kanagawa, Japan} % Location
    {2011-2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Hosted an experimental farming project: spot-hosting abandoned fields for the locals and education of practical agriculture.}
        \item {Produced Edamame beans with a support of local farms and sold at festival markets.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
