%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Selected Presentation}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {26th Auto-ID Laboratory China-Japan-Korea-Taiwan Joint Workshop} % Role
    {{\fontsize{8pt}{1em}\bodyfont\slshape\color{graytext} Iori Mizutani} "Entropy Filter for High Performance RFID Middleware"} % Event
    {Kanagawa, Japan} % Location
    {Nov. 2017} % Date(s)
    {
      \begin{cvitems}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {In Proceedings of the 7th International Conference on the Internet of Things (IoT’17). ACM \url{https://web.sfc.wide.ad.jp/~iomz/cv/files/IoT_2017_ar_semantics.pdf}} % Role
    {{\fontsize{8pt}{1em}\bodyfont\slshape\color{graytext} Iori Mizutani, Mareike Kritzler, Kimberly Garcia, Florian Michahelles} "Intuitive Interaction with Semantics using Augmented Reality – a Case Study of Workforce Management in an Industrial Setting"} % Event
    {Linz, Austria} % Location
    {Oct. 2017} % Date(s)
    {
      \begin{cvitems}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {25th Auto-ID Laboratory China-Japan-Korea-Taiwan Joint Workshop \*Best Speaker Award} % Role
    {{\fontsize{8pt}{1em}\bodyfont\slshape\color{graytext} Iori Mizutani} "Cross-Domain Information Access through AR Interface"} % Event
    {Taipei, Taiwan} % Location
    {May. 2017} % Date(s)
    {
      \begin{cvitems}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {In Proceedings of the 6th International Conference on the Internet of Things (IoT’16). ACM \url{https://web.sfc.wide.ad.jp/~iomz/cv/files/IoT_2016_emu.pdf}} % Role
    {{\fontsize{8pt}{1em}\bodyfont\slshape\color{graytext} Iori Mizutani and Jin Mitsugi} "A Multicode and Portable RFID Tag Events Emulator for RFID Information System"} % Event
    {Stuttgart, Germany} % Location
    {Nov. 2016} % Date(s)
    {
      \begin{cvitems}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Institute of Electronics, Information and Communication Engineers(IEICE) Society Conference 2016} % Role
    {{\fontsize{8pt}{1em}\bodyfont\slshape\color{graytext} Haruka Kuji, Iori Mizutani, Jin Mitsugi} "An MLE-based RFID Tag Localization with Mechanically Controlled Antenna"} % Event
    {Hokkaido, Japan} % Location
    {Sep. 2016} % Date(s)
    {
      \begin{cvitems}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Bachelor Thesis \url{https://web.sfc.wide.ad.jp/~iomz/cv/files/iomz_b_thesis.pdf}} % Role
    {{\fontsize{8pt}{1em}\bodyfont\slshape\color{graytext} Iori Mizutani} "A Novel RFID Filtering and Collection Middleware to Accommodate Different International Unique Identifier Standards"} % Event
    {Kanagawa, Japan} % Location
    {Jan. 2016} % Date(s)
    {
      \begin{cvitems}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {6th Annual IEEE International Conference on RFID Technology and Applications(RFID-TA) \*Nominated for Best Student Paper \url{https://web.sfc.wide.ad.jp/~iomz/cv/files/IEEE_RFIDTA_2015_multicode.pdf}} % Role
    {{\fontsize{8pt}{1em}\bodyfont\slshape\color{graytext} Iori Mizutani, Jin Mitsugi, Masaki Ehara, Hiroyuki Suzuki} "Multi-code Filtering and Collection : Proposal and Performance Evaluation"} % Event
    {Tokyo, Japan} % Location
    {Sep. 2015} % Date(s)
    {
      \begin{cvitems}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Tokuda-Murai Joint Laboratory Presentation \url{https://web.sfc.wide.ad.jp/~iomz/cv/files/hearty_drinker.pdf}} % Role
    {{\fontsize{8pt}{1em}\bodyfont\slshape\color{graytext} Iori Mizutani} "Estimation of Personalized Blood Concentration Transition for Therapeutic Drug Monitoring"} % Event
    {Kanagawa, Japan} % Location
    {Jan. 2015} % Date(s)
    {
      \begin{cvitems}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {NICT FIRST Annual conference} % Role
    {{\fontsize{8pt}{1em}\bodyfont\slshape\color{graytext} Iori Mizutani, Koji Murata} "Prototyping QKD BB84 protocol with Laser and Polarization filter" \url{https://web.sfc.wide.ad.jp/~iomz/cv/files/qkd_poster.pdf}} % Event
    {Tokyo, Japan} % Location
    {Dec. 2012} % Date(s)
    {
      \begin{cvitems}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Keio University SFC Open Research Forum 2011 \url{https://web.sfc.wide.ad.jp/~iomz/cv/files/qkd_3d_anime.mp4}} % Role
    {{\fontsize{8pt}{1em}\bodyfont\slshape\color{graytext} Iori Mizutani} "3D Animation of Quantum Key Distribution"} % Event
    {Tokyo, Japan} % Location
    {Nov. 2011} % Date(s)
    {
      \begin{cvitems}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
